---
title: "Plotly: NY NOAA"
output: 
  html_document:
    toc: true
    toc_float: true
---
# Loading data
We're gonna look at NY NOAA data. 

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

```{r}
data("ny_noaa")
ny_noaa_tidy = ny_noaa %>% 
  separate(date, 
           into = c("year","month","day"), 
           sep = "-") %>% 
  mutate_at(vars(year,month,day), as.factor) %>% 
  mutate_at(vars(tmax, tmin, prcp, snow, snwd), as.numeric) %>% 
  mutate(tmax = tmax / 10,
         tmin = tmin / 10,
         prcp = prcp / 10) %>% 
  sample_n(3000, replace = F)
```

# Plotly plots

## Scatterplot - Min vs Max Tempatures in NY

```{r, warning = F, message = F}
ny_noaa_tidy %>% 
  mutate(text_label = str_c("Year: ", year,
                            "\nMonth: ", month)) %>% 
  plot_ly(x = ~tmax, 
          y = ~tmin, 
          type = "scatter", 
          mode = "markers",
          alpha = .5, 
          color = ~year, 
          text = ~text_label,
          colors = "viridis")
```

## Boxplot - Distribution of Snowfall in NY
values > 0 and < 100 separately by year

```{r, warning = F, message = F}
ny_noaa_tidy %>%
    filter(snow > 0 & snow < 100) %>%
    group_by(year) %>%
    mutate(text_label = str_c("Year: ", year, 
                              "\n Snowfall(mm): ", snow)) %>%
    plot_ly(x = ~year, 
            y = ~snow, 
            color = ~year, 
            type = "box", 
            text = ~text_label,
            colors = "viridis")
```

## Bar plot - Distributions of Avage Precipitation in NY

```{r, warning = F, message = F}
ny_noaa_tidy %>%
  filter(prcp > 0) %>%
  group_by(year) %>%
  summarize(avg_prcp = mean(prcp)) %>% 
  mutate(text_label = str_c("Year: ", year, 
                              "\nMean\nPrecipitation(mm): ", avg_prcp)) %>%
    plot_ly(x = ~year, 
            y = ~avg_prcp, 
            color = ~year, 
            type = "bar", 
            text = ~text_label,
            colors = "viridis")
```
